### 2013-09-16 thesis/src/chapters/chapter-5.tex
Added arch of csap

\chapter{Solution}

@@

Taking requirements into consideration, desired platform clearly has features common to a autonomic system, especially the need for automatic environment reconfiguration. One of the first architectures that satisfied that requirement was proposed by \cite{IBM06}. Beside this, system under consideration has a character of a multi-layered one (i.e. it operates on a application / container / service / cloud level). Optimally, each level should be characterized by different actions, what can be meet by implementing multi-hierarchical autonomic system, as proposed in \cite{LiWoZh05}.

Considering that observation, auto-scaling subsystem spans across different layers:

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=\textwidth]{chapter-5/hierarchical-autonomic-system}
  \end{center}
  \caption{Hierarchical autonomic system}
  \label{ch5:hierarchical-autonomic-system}
\end{figure}

Remaining of this section breaks apart each functional module of an autonomic component, whereas further sections cover in details each autonomic level.

\subsection{Autonomic component}

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=0.8\textwidth]{chapter-5/autnomic-component}
  \end{center}
  \caption{Autonomic component}
  \label{ch5:autonomic-component}
\end{figure}

\subsubsection{Monitor}

Monitor module is responsible for gathering monitoring data from \textit{Sensors} and store them in a database, correlated with a specific autonomous component (ie. application / container / service / cloud). Problem of a multi-layered, hierarchical self-adaptive monitoring system is described in \cite{KaKoGoKyMeVa12}.

\subsubsection{Analyse}

Analyse module performs analysis of a gathered data. There is a variety of models that helps to achieve this goal. For example, the \cite{LiWoZh05} proposes:

\begin{itemize}
	\item Queue-based Performance Models
	\item Dynamic models
	\item Monotonic static models
	\item Policy based models
\end{itemize}

Details about which level leverage which model are presented in detailed architecture description. Important part in a data analysis plays a predictive approach \cite{JiPeLiCh11} and tracking changes in a system \cite{ZhYaWo05}.

\subsubsection{Plan}

This module is responsible for scheduling actions that have to be taken to solve problems reported by an earlier analysis. This may involve:
\begin{itemize}
	\item reserving some resources (for example to deploy a new virtual machine)
	\item handling situation where multiple entities compete about the resources (for example by a prioritization)
\end{itemize}

It is possible, however, that resolving issues is not possible at current level. It that case, the upper-level is responsible for handling it.

\subsubsection{Execute}

Execute module is directly responsible for managing resource, by performing various operations on resource's effector. Each layer is characterized by different actions that can be taken, for example: application server reconfiguration, vertical or horizontal scaling.

\subsubsection{Knowledge base}

Knowledge base is represented as a set of rules, policies shared across autonomous components.

\subsection{Managed resource}

\subsubsection{Effector}

Enables management of a resources by exposing some API compatible with an Executor.

\subsubsection{Sensor}

Aim of a sensor is probing a resource and sending back results to a Monitor. There are different kind of metrics that should be considered such as: CPU load, memory usage or response delay.

\section{Application controller}

\section{Container controller}

\section{Service controller}

\section{Cloud controller}

>>>>

\chapter{Architecture of Cloud-SAP}

\chapterintro{This chapter introduces architecture of Cloud-SAP, Platform-as-a-Service model that aims to satisfy requirements introduced in first chapter.}

@@

One can notice that elements that yields a solution for a problem stated in first chapter, which is ensuring that users' application provide appropriate Quality-of-Service for its customers, were introduced in previous chapters:
\begin{itemize}
	\item scalability - ability to improve application performance by enriching 
	\item adaptivity - ability to adapt (i.e. scale) appropriately to current usage pattern
	\item inter-cloud awareness - ability to cooperate with different cloud provider to supply application with extra resources
\end{itemize}

To begin with, different scalability models were introduced. Noticeably, they operated at different layers: 
\begin{itemize}
	\item application platform tuning
	\item single-server level (vertical scaling)
	\item multi-server level (horizontal scaling) 
	\item inter-cloud level (scaling out across different cloud-providers, concept introduced in previous chapter)
\end{itemize}
Consequently, it is expected that proposed solution's architecture reflects that multi-layered model, which, as Table \ref{tab:cloud-providers-scaling} illustrates, hasn't been yet introduced to the marked. Additionally, each layer has to be characterized by an ability to adapt to a given application usage. As previous chapter stated, this can be achieved by adding a elasticity controller to each layer. This observation is a foundation of proposed architecture.

One of the first models that ensured system adaptivity is an autonomic component, concept based on a feed-back loop, initially proposed by IBM \cite{IBM06}. Figure () depicts that architecture.

Since designed platform operates on multiple layers, we can extend that model by using concept of a multi-hierarchical autonomic system \cite{LiWoZh05}. Figure () illustrates that hierarchy, were each level represents a different perspective at application scaling. Using terminology characteristic to a autonomic system, first three hierarchy levels (application tuning, single-server, multi-server) are centralized and controlled by single elasticity controller at each level, while the last inter-cloud level is a decentralized one - each cloud instance is fully independent.

As \cite{IBM06} states, each autonomic component has modules that are responsible for:
\begin{itemize}
	\item monitoring
	\item analysis
	\item planning
	\item action execution
\end{itemize}

While the managed component has:
\begin{itemize}
	\item sensors
	\item effectors
\end{itemize}

Due to the hierarchy of our architecture, each level manages an underlying autonomic component, while being managed by an upper layer at the same time. This lead us to observation that they are autonomic components and managed components at the same time. Remaining of this chapter discusses in detail each layer taking into account that observation.
